How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-27 tse-paper/content.tex
Include lit overview schematic

\begin{table}[]
\centering
\caption{Overview of the described chunk retrieval techniques.}
\begin{tabularx}{\columnwidth}{@{}XlXlX@{}} 
\toprule
Name                         & Acronym & Identification Technique                                   & Granularity & Configuration             \\ 
\midrule
Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, expected number of lines & Line        & Output examples           \\
Keyword Search               & KWS     & Keywords, expected number of lines                    & Line        & Keywords, context length  \\
Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
Diff Approach                & ---     & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
\bottomrule
\end{tabularx}
\label{tab:ctr}
\end{table}

@@

\section{Systematic Literature Survey and Mapping}
\label{sec:survey}
% TODO (Caro): Integrate Kitchenham's guidelines
From our own experience, we know that the field of analyzing build
logs is relatively young, with perhaps the work on TravisTorrent the
most cited and central one. We also know there have been scattered
research efforts on build log analysis prior to it, mostly where the
log analysis was a side-part of the article. To the best of our
knowledge, there has not been an attempt to systematically overview
and survey them, despite their forseeable future and current practical
importance.

\subsection{Selection Protocol}
In this first overview, we therefore want to survey as broad a
population of scientific material as possible. Note that we do not
limit our sources to a handful of Software Engineering venues, as is
often done, but survey all sources monitored by Google Scholar,
including Bachelor's and Master's theses, academic slide decks, and
books. We use Google Scholar as opposed to Scopus or other databases,
as it is the search engine for acdemic articles with the broadest and
most current index, including preprints from sources such as
arXiv. One challenge is that no common nomenclature has been
established yet (in fact, this is one of the goals of this article).

@@

To make handling so many search results feasible, the authors of the
paper employed a two-pass filtering strategy:

>>>>

\begin{table*}[]
\centering
\caption{Overview of the described chunk retrieval techniques.}
\begin{tabularx}{\textwidth}{@{}XlXlXX@{}} 
\toprule
Name                         & Acronym & Identification Technique                                   & Granularity & Configuration & Source            \\ 
\midrule
Program Synthesis by Example & PBE     & Regular expression program                                 & Character   & In/output examples      \\
Common Text Similarity       & CTS     & TF-IDF \& cosine similarity, expected number of lines & Line        & Output examples           \\
Keyword Search               & KWS     & Keywords, expected number of lines                    & Line        & Keywords, context length  \\
Random Line Retrieval        & RLR     & Random sample                                              & Line        & Retrieval length          \\
Diff Approach                & ---     & Line not present in successful log, information retrieval  & Line        & Logs from failing and successful builds      \\
\bottomrule
\end{tabularx}
\label{tab:ctr}
\end{table*}

@@

\section{Systematic Literature Survey and Mapping}
\label{sec:survey}
% TODO (Caro): Integrate Kitchenham's guidelines
From our own experience, we know that the field of analyzing build
logs is relatively young, with perhaps the work on TravisTorrent the
most cited and central one. We also know there have been scattered
research efforts on build log analysis prior to it, mostly where the
log analysis was a side-part of the article. To the best of our
knowledge, there has not been an attempt to systematically overview
and survey them, despite their forseeable future and current importance.

\subsection{Study Selection}

\begin{figure}[htb]
		\centering
		\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
		\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
		\label{fig:lit-survey}
\end{figure}
\Cref{fig:lit-survey} presents an overview of our study selection.
In this first literature overview study on analyzing build logs, we
therefore want to survey as broad a population of scientific material
as possible. Note that we do not limit our sources to specific
Software Engineering venues, as is often done, but survey all sources
monitored by Google Scholar, including Bachelor's and Master's theses,
academic slide decks, and books. We use Google Scholar as opposed to
Scopus or other databases, as it is the search engine for acdemic
articles with the broadest and most current index, including preprints
from sources such as arXiv. One challenge is that no common
nomenclature has been established yet (in fact, this is one of the
goals of this article).

@@

To make handling so many search results feasible, we employed a
two-pass filtering strategy:
